Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-07 csf-2017/paper.tex
Tune math sizes in the same way as for the EuroS&P2016 paper.
region intuition

@@

\subsubsection{Future worlds}

{\bf Public future worlds}
The \emph{public future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi_\pub \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurewk (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ (\temp,s,\phi_\pub,\phi,H) \in \Regions }
  { (\temp,s,\phi_\pub,\phi,H) \futurewk \revoked }
  \and
  \inferrule{ }
  { \revoked \futurewk \revoked }
\end{mathpar}

{\bf Private future worlds}

The \emph{private future} region relation satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurestr (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr (\temp,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr \revoked }
\end{mathpar}

The two future world relations satisfy the following properties: They allow for any extension of the current world and all existing worlds are allowed to move to an appropriate future region. That is
\begin{mathpar}
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurewk W(r) }
  { W' \futurewk W }
  \and
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurestr W(r) }
  { W' \futurestr W }
\end{mathpar}

>>>>

\subsection{Regions}
%Regions intuition
We have three types of regions: $\perma$, $\temp$, and $\revoked$. The
$\perma$ and $\temp$ regions contains a state transition system with
public and private transitions as known from logical relations
from high-level languages\todo{reference}. The state transition
systems can be understood as protocols the memory must follow. The
protocols imposed on memory by $\perma$ regions stay in place
indefinitely. This means that any capability, $\local$ or $\glob$, can
depend on these protocols. The protocols imposed on memory by $\temp$
regions can be revoked at certain points during execution
corresponding to the points when $\local$ capabilities can be
revoked. This means that $\local$ capabilties safely can depend on the
protocols imposed on memory by $\temp$ regions, but $\glob$
capabilities cannot as the $\glob$ capability may stay around
throughout the execution of a program, but the $\temp$ regions may not
stay around.

For monotonicity reasons, a region cannot disappear, but
we need a way to remove $\temp$ regions. This is where the $\revoked$ region comes
into the picture. The $\revoked$ region contains no state transition
system and puts no requirements on the memory it models. It serves
simply as a mask for the $\temp$ regions that have been revoked.

@@

\subsubsection{Future worlds}
There are two future world relations a \emph{public future world} relation and a \emph{private future world} relation. In both future world relations, we have extension ordering, so a future world $W'$ of $W$ has at least the same regions as $W$, but it may add new regions imposing new protocols on part of the memory. The two future world relations differ in the way existing regions are allowed to evolve. In a \emph{public future region} 
\begin{mathpar}
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurewk W(r) }
  { W' \futurewk W }
  \and
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurestr W(r) }
  { W' \futurestr W }
\end{mathpar}

{\bf Public future regions}
The \emph{public future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi_\pub \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurewk (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ (\temp,s,\phi_\pub,\phi,H) \in \Regions }
  { (\temp,s,\phi_\pub,\phi,H) \futurewk \revoked }
  \and
  \inferrule{ }
  { \revoked \futurewk \revoked }
\end{mathpar}

{\bf Private future regions}
The \emph{private future} region relation satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurestr (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr (\temp,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr \revoked }
\end{mathpar}

The two future world relations satisfy the following properties: They allow for any extension of the current world and all existing worlds are allowed to move to an appropriate future region. That is
